Development of Performance Regression Analysis Tool using Distributed Tracing on microservice-based Application\\

### 2022-09-07 paper.tex
txs auto checkin

\begin{abstract}
In applications with Microservice architecture, when a significant change occurs and result in decreased performance or regression, it is difficult to perform analysis to check which part of the whole Microservice is the main cause of the regression due to the distributed nature of Microservice. Distributed tracing can be used to analyze and determine whether there is a regression and the cause of the regression by utilizing latency data from existing operations on Microservice application.
This system will perform performance regression analysis using the distributed tracing tool Zipkin. Regression is then can be detected using Kolmogorov-Smirnov statistical analysis which will compare the latency data samples that occur
periodically and the sample latency baseline data that represents application performance  under normal circumstances. The analysis will compare the Cumulative
Distribution Function (CDF) of the two samples and see if both
CDF comes from a different distribution. If it is found that both CDFs originate from different distributions, it then can be suspected that there has been a performance regression because the distribution of the periodic data has deviated from the distribution of the baseline data.
If a regression is detected, the system will then perform a critical path analysis to see which operations of each services are most likely contributed to the regression. The analysis will be executed by finding the difference
latency of periodic and baseline operation data and it will be seen which operation's latency difference exceeds a predetermined limit.
The performance regression analysis system has been tested on a Microservice application that runs on Kubernetes. The result is that out of 10 out of 11 test cases, and for every successful case, the main suspected operation that causes regression is found. Implementing the system adds an average overhead of 0.78\% CPU usage and 0.67\% Memory usage.
\end{abstract}

\begin{IEEEkeywords}
performance regression, Distributed Tracing, Microservice, Kubernetes
\end{IEEEkeywords}

\section{Introduction}
\label{1}
With the widespread adoption use of Microservice architecture based on distributed systems today, more and more challenges arise related to the adoption of this architectural style. Microservice architecture offers several advantages, including technological heterogeneity, resilience, ease of \textit{scaling}, ease of \textit{deployment}, ease of alignment with a technology team, flexibility in determining application composition, and an optimized system to replace components with each other \cite{building-microservices}. These advantages make the adoption of the Microservice architecture quite widespread, especially in applications that require \textit{scalability} to serve the growing needs of customers.

However, with the many advantages offered by the Microservice architecture, it will also increase the complexity to perform analysis when there is a decline in performance or regression in the application. This is due to the distributed nature of Microservice by dividing the application into smaller services, so to find which operation of the services causing the regression will be difficult and will be inefficient to perform analysis on each and every available services, especially if the number of the services has reached hundreds or thousands.

There is already a tool that can help developers to perform monitoring on distributed systems such as Microservice, which is distributed tracing. With the help of trace, developers can get an overview of each request that occurs in a resource or component that interacts with other components in a distributed system such as node, service, network, or mutex. The traces then can be processed for various purposes, such as creating a dependency map between services, perform a performance analysis of the service, and also perform a performance regression analysis using the latency data from the trace result.

For this paper, the performance metric that will be analyzed from the microservice-based application is limited to latency performance only. The latency data is one of the default data provided by several distributed tracing tools, so the performance regression that will be analyzed in this paper is only related to latency of the API calls performed by the services inside the microservice application.

We provide the implementation of the performance regression analysis (PRA) system using the distributed tracing tool Zipkin which is available on Github\footnote{\url{https://github.com/masterraf21/pra\textunderscore engine}}. The PRA system will perform detection on the Microservice application when a regression occurs and perform analysis to determine the main cause of the regression. Performance regression analysis will be done by using the help of the trace results from Zipkin which will be able to help developers restore performance of Microservice application after reggresion occurs.

@@

%Given the distributed nature of Microservices, it will be difficult for developers if regression detection is executed with an individual approach on each existing servce especially when the number of existing servce is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in microservice-based application, an approach that does not require developers to source search is needed. So that in the case of detection and regression analysis of microservice-based application performance, the first approach is more suitable to use.
Given the distributed nature of microservices, it will be difficult for developers if regression detection is executed with an individual approach on each existing service especially when the number of existing service is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in microservice-based application, an approach that does not require developers to source search is needed. With the help of distributed tracing tool, performance related data from multiple services in a distributed microservice-based application can be collected and analyzed in a single collective source, so that the developer should not be worried about analyzing each and every service available to perform regression related problem, rather they can rely on the data provided from the distributed tracing tool to analyze the whole microservice-based application. In the case of detection and regression analysis of microservice-based application performance, the first approach is more suitable to use.

Therefore, the workflow that must be executed by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in microservice-based application
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}

@@

Cumulative Analysis is an approach to analyze certain metrics of application such as latency by cummulating all the collected data as a single representation such as Histogram. With this approach, the distributed nature of many services in microservice-based application can be observed as a single figure or representation so that the whole Microservice application can be monitored in a single space. To use this approach, all the latency data acquired from the distributed tracing will be collected and converted into a Cumulative Distribution Function (CDF). Cumulative Distribution Function is a function whose value is the probability that a corresponding continuous random variable has a value less than or equal to the argument of the function. This statistical function is useful to represent a set of corresponding data into a single quantifiable function which can be useful as a comparison tool.

One of the available tool to analyze and compare large sets of data is called Kolmogorov-Smirnov (K-S) statistic test. The K-S statistic test will count the difference between two CDFs as a scalar number \cite{kolmogorov_1951}. K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on pattern of the data represented, for example the latency performance of a microservice-based application.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.35\textwidth]{resources/ch2/ks.png}
	\caption{CDF of two samples, arrows indicate the Kolmogorov-Smirnov statistical value \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

@@

\section{Conclusion \& Future Works}
The implemented performance regression analysis system can detect and analyze the cause of regression on microservice-based application using Kolmogorov-Smirnov test and Critical Path analysis. However, the Kolmogorov-Smirnov test alone cannot determine exactly whether the detected regression is caused by internal or external factors, therefore the Critical Path analysis is required to help determine the exact cause of the regression.

>>>>

\begin{abstract}
In applications with microservice architecture, when a significant change occurs and result in decreased performance or regression, it is difficult to perform analysis to check which part of the whole microservice is the main cause of the regression due to the distributed nature of microservice. Distributed tracing can be used to analyze and determine whether there is a regression and the cause of the regression by utilizing latency data from existing operations on microservice application.
This system will perform performance regression analysis using the distributed tracing tool Zipkin. Regression is then can be detected using Kolmogorov-Smirnov statistical analysis which will compare the latency data samples that occur
periodically and the sample latency baseline data that represents application performance  under normal circumstances. The analysis will compare the Cumulative
Distribution Function (CDF) of the two samples and see if both
CDF comes from a different distribution. If it is found that both CDFs originate from different distributions, it then can be suspected that there has been a performance regression because the distribution of the periodic data has deviated from the distribution of the baseline data.
If a regression is detected, the system will then perform a critical path analysis to see which operations of each services are most likely contributed to the regression. The analysis will be executed by finding the difference
latency of periodic and baseline operation data and it will be seen which operation's latency difference exceeds a predetermined limit.
The performance regression analysis system has been tested on a microservice application that runs on Kubernetes. The result is that out of 10 out of 11 test cases, and for every successful case, the main suspected operation that causes regression is found. Implementing the system adds an average overhead of 0.78\% CPU usage and 0.67\% Memory usage.
\end{abstract}

\begin{IEEEkeywords}
performance regression, Distributed Tracing, microservice, Kubernetes
\end{IEEEkeywords}

\section{Introduction}
\label{1}
With the widespread adoption use of microservice architecture based on distributed systems today, more and more challenges arise related to the adoption of this architectural style. Microservice architecture offers several advantages, including technological heterogeneity, resilience, ease of \textit{scaling}, ease of \textit{deployment}, ease of alignment with a technology team, flexibility in determining application composition, and an optimized system to replace components with each other \cite{building-microservices}. These advantages make the adoption of the microservice architecture quite widespread, especially in applications that require \textit{scalability} to serve the growing needs of customers.

However, with the many advantages offered by the microservice architecture, it will also increase the complexity to perform analysis when there is a decline in performance or regression in the application. This is due to the distributed nature of microservice by dividing the application into smaller services, so to find which operation of the services causing the regression will be difficult and will be inefficient to perform analysis on each and every available services, especially if the number of the services has reached hundreds or thousands.

There is already a tool that can help developers to perform monitoring on distributed systems such as microservice, which is distributed tracing. With the help of trace, developers can get an overview of each request that occurs in a resource or component that interacts with other components in a distributed system such as node, service, network, or mutex. The traces then can be processed for various purposes, such as creating a dependency map between services, perform a performance analysis of the service, and also perform a performance regression analysis using the latency data from the trace result.

For this paper, the performance metric that will be analyzed from the microservice application is limited to latency performance only. The latency data is one of the default data provided by several distributed tracing tools, so the performance regression that will be analyzed in this paper is only related to latency of the API calls performed by the services inside the microservice application.

We provide the implementation of the performance regression analysis (PRA) system using the distributed tracing tool Zipkin which is available on Github\footnote{\url{https://github.com/masterraf21/pra\textunderscore engine}}. The PRA system will perform detection on the microservice application when a regression occurs and perform analysis to determine the main cause of the regression. Performance regression analysis will be done by using the help of the trace results from Zipkin which will be able to help developers restore performance of microservice application after reggresion occurs.

@@

%Given the distributed nature of Microservices, it will be difficult for developers if regression detection is executed with an individual approach on each existing servce especially when the number of existing servce is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in microservice application, an approach that does not require developers to source search is needed. So that in the case of detection and regression analysis of microservice application performance, the first approach is more suitable to use.
Given the distributed nature of microservices, it will be difficult for developers if regression detection is executed with an individual approach on each existing service especially when the number of existing service is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in microservice application, an approach that does not require developers to source search is needed. With the help of distributed tracing tool, performance related data from multiple services in a distributed microservice application can be collected and analyzed in a single collective source, so that the developer should not be worried about analyzing each and every service available to perform regression related problem, rather they can rely on the data provided from the distributed tracing tool to analyze the whole microservice application. In the case of detection and regression analysis of microservice application performance, the first approach is more suitable to use.

Therefore, the workflow that must be executed by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in microservice application
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}

@@

Cumulative Analysis is an approach to analyze certain metrics of application such as latency by cummulating all the collected data as a single representation such as Histogram. With this approach, the distributed nature of many services in microservice application can be observed as a single figure or representation so that the whole microservice application can be monitored in a single space. To use this approach, all the latency data acquired from the distributed tracing will be collected and converted into a Cumulative Distribution Function (CDF). Cumulative Distribution Function is a function whose value is the probability that a corresponding continuous random variable has a value less than or equal to the argument of the function. This statistical function is useful to represent a set of corresponding data into a single quantifiable function which can be useful as a comparison tool.

One of the available tool to analyze and compare large sets of data is called Kolmogorov-Smirnov (K-S) statistic test. The K-S statistic test will count the difference between two CDFs as a scalar number \cite{kolmogorov_1951}. K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on pattern of the data represented, for example the latency performance of a microservice application.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.35\textwidth]{resources/ch2/ks.png}
	\caption{CDF of two samples, arrows indicate the Kolmogorov-Smirnov statistical value \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

@@

\section{Conclusion \& Future Works}
The implemented performance regression analysis system can detect and analyze the cause of regression on microservice application using Kolmogorov-Smirnov test and Critical Path analysis. However, the Kolmogorov-Smirnov test alone cannot determine exactly whether the detected regression is caused by internal or external factors, therefore the Critical Path analysis is required to help determine the exact cause of the regression.
